A Hitchhiker's Guide to Reproducible Research in R

### 2021-07-06 manuscript.Rmd
change how r code is presented

These results are based on simulated data.

```{r, results='asis'}
set.seed(112358) # fix state of RNG
report::report_text(
  planned_analysis(
    simulate_data(
      n = 400,# Sample size
      df = 8, # Chisq with DF = 8 has skewness = 1
      d = .2, # Cohen's D
      i = 10  # Number of items (should not effect anything)
    )
  )$test
)
```

>>>>

```{r, results='asis'}
set.seed(112358) # fix state of RNG
results <- 
  planned_analysis(
    simulate_data(
      n = 400,# Sample size
      df = 8, # Chisq with DF = 8 has skewness = 1
      d = .2, # Cohen's D
      i = 10  # Number of items (should not effect anything)
    )
  )
```

These results are based on simulated data:

```{r}
report::report(results)
```
